### 2025-03-11 evaluating-prediction-accuracy.qmd
202503011 - clean up link

The adapted formula for MASE with non-time series data is described by @Hyndman2014 [here (https://stats.stackexchange.com/a/108963/20338)](https://stats.stackexchange.com/a/108963/20338) (archived at https://perma.cc/G469-8NAJ).
Scaled errors are calculated using @eq-scaledError:

>>>>

The adapted formula for MASE with non-time series data is described by @Hyndman2014 at the following link: <https://stats.stackexchange.com/a/108963/20338> (archived at <https://perma.cc/G469-8NAJ>).
Scaled errors are calculated using @eq-scaledError:
